An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-09 EconGrowth.Rnw
Now generating SF cloud graphs in the paper.

\section*{To-do List}
\begin{itemize}
\item{Heun: Figure out why CESe for ZA with X fails during resampling.}
\item{Heun: Review all assumptions for CES with energy models. 
There are several assumptions for rho and rho1 for various countries. 
When we are resampling, we probably don't want to specify those values.}
\item{Heun: Implement confidence interval calculations for 
all resampling methods.}
\item{Heun: Decide if the single factor models should include constraints
on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}
\item{Heun: Make smaller cloud plots for resample coefficients for those 
countries where $u$ is involved.}
\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
\item{Heun: Get AIC calculations working again.}
\item{Heun: Fix the energy sankey diagram from the seminar}
\item{Heun: Include adjusted sankey diagram in the seminar}
\item{Heun: Add CES production function fits}
      \begin{itemize}
      \item{Write up the decisions about parameter estimation for the 
            CES production function fits}
      \item{Revisit my assumptions for the CES production function 
            (with energy) for each country.}
      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
            the CES parameter tables in the appendix}
      \item{Add CES rows to the AIC table. Code is in the 
            \texttt{createAICTable} function, but it is not yet working. 
            Need to find a way to calculate AIC for the object that is 
            returned from the \texttt{cesEst} function.}
      \end{itemize}
\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
\item{de Wit: review, critique, and contextualize.}
\end{itemize}

@@

>>>>

\section*{To-do List}
\begin{itemize}
\item{Heun: Add option for $m = 1$ in single-factor models.}
\item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
\item{Heun: Review all assumptions for CES with energy models. 
There are several assumptions for rho and rho1 for various countries. 
When we are resampling, we probably don't want to specify those values.}
\item{Heun: Re-implement confidence interval calculations to use
resampling methods.}
      \begin{itemize}
      \item{SF}
      \item{CD}
      \item{\st{CDe}}
      \item{CES}
      \item{CESe}
      \item{LINEX}
      \end{itemize}
\item{Heun: Include cloud graphs for model parameters 
estimated by resampling methods.}
      \begin{itemize}
      \item{\st{SF}}
      \item{CD}
      \item{\st{CDe}}
      \item{CES}
      \item{CESe}
      \item{LINEX}
      \end{itemize}
\item{\st{Heun: Decide if the single factor models should include constraints
on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
\item{\st{Heun: Make smaller cloud plots for resample coefficients for those 
countries where $u$ is involved.}}
\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
\item{Heun: Get AIC calculations working again.}
\item{Heun: Fix the energy sankey diagram from the seminar}
\item{Heun: Include adjusted sankey diagram in the seminar}
\item{Heun: Add CES production function fits}
      \begin{itemize}
      \item{Write up the decisions about parameter estimation for the 
            CES production function fits}
      \item{Revisit my assumptions for the CES production function 
            (with energy) for each country.}
      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
            the CES parameter tables in the appendix}
      \item{Add CES rows to the AIC table. Code is in the 
            \texttt{createAICTable} function, but it is not yet working. 
            Need to find a way to calculate AIC for the object that is 
            returned from the \texttt{cesEst} function.}
      \end{itemize}
\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
\item{de Wit: review, critique, and contextualize.}
\end{itemize}

@@

Coefficients derived from resampling are shown in 
Figures~\ref{fig:SFk_Resample_Graph}--\ref{fig:SFu_Resample_Graph}. 
In each case, the exponent on the factor of production is assumed to be $m = 1$.

<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.">>=
sfResamplePlot(factor="K")
@

<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.">>=
sfResamplePlot(factor="L")
@

<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.">>=
sfResamplePlot(factor="Q")
@

<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.">>=
sfResamplePlot(factor="X")
@

<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.">>=
sfResamplePlot(factor="U")
@
